\textbf{ Joystream: A Protocol for User Governed Content Platforms }

### 2019-02-25 paper.tex
Add "a"
Here it's gigabytes, later bytes. The unit should be part of the value, to allow conversion. For simplicity, let's just stick to "bytes" and leave the details up to the implementation/later specs.

As mentioned before, for example in section \ref{sec:member}, it should be possible to onboard users who do not hold any tokens. This activity, which is called \textit{screening}, allows the platform to accommodate new users who can try the platform within certain constraints. However, the combination of no robust identity system and allowing users to consumer resources without paying on the margin creates its own set of new problems. These resources need not only be in the form of tangibles like compute and storage, but also things like peer member attention. Not only does this result in wasteful overutilisation, but perhaps more importantly, it allows platform participants to shape their own payouts by at a low cost, since resource use is often tied to payouts. For example viewing content will divert larger share of payout to the publisher.

@@

\begin{concept_box}{Storage Provider Tranche}
    \begin{itemize}
      \item[-] \textbf{ID:} Unique integer identifier.
      \item[-] \textbf{Capacity:} The number of gigabytes of storage capacity which is required.
      \item[-] \textbf{Out Speed:} The number of Mbps out which are required.
      \item[-] \textbf{Stake:} The amount of stake required.
      \item[-] \textbf{Duration:} The number of blocks service must be provided from initiation block.
      \item[-] \textbf{Fixed Reward:} Quantity of native token earned per unit of time.
      \item[-] \textbf{Variable Reward:} Quantity of native token earned per unit of date stored.
      \item[-] \textbf{Slots:} Total number of roles available in this tranche.
      \item[-] \textbf{Terms:} String of capped length (UTF-8) describing the human readable conditions which are being agreed upon.
      \item[-] \textbf{Active:} Whether tranche is actually possible to use, that is assign new members to.
    \end{itemize}
\end{concept_box}

>>>>

As mentioned before, for example in section \ref{sec:member}, it should be possible to onboard users who do not hold any tokens. This activity, which is called \textit{screening}, allows the platform to accommodate new users who can try the platform within certain constraints. However, the combination of no robust identity system and allowing users to consumer resources without paying on the margin creates its own set of new problems. These resources need not only be in the form of tangibles like compute and storage, but also things like peer member attention. Not only does this result in wasteful overutilisation, but perhaps more importantly, it allows platform participants to shape their own payouts by at a low cost, since resource use is often tied to payouts. For example viewing content will divert a larger share of payout to the publisher.

@@

\begin{concept_box}{Storage Provider Tranche}
    \begin{itemize}
      \item[-] \textbf{ID:} Unique integer identifier.
      \item[-] \textbf{Capacity:} The number of bytes of storage capacity which is required.
      \item[-] \textbf{Out Speed:} The number of Mbps out which are required.
      \item[-] \textbf{Stake:} The amount of stake required.
      \item[-] \textbf{Duration:} The number of blocks service must be provided from initiation block.
      \item[-] \textbf{Fixed Reward:} Quantity of native token earned per unit of time.
      \item[-] \textbf{Variable Reward:} Quantity of native token earned per unit of date stored.
      \item[-] \textbf{Slots:} Total number of roles available in this tranche.
      \item[-] \textbf{Terms:} String of capped length (UTF-8) describing the human readable conditions which are being agreed upon.
      \item[-] \textbf{Active:} Whether tranche is actually possible to use, that is assign new members to.
    \end{itemize}
\end{concept_box}
